Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-04-01 manuscript/manuscript_pve.Rmd
automated package installing if not installed already

@@

\
An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot]. Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root]. Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth]. A meta-analysis by Poorter et al. [-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used. This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower C exchange and assimilate export rates [@robbins1988effect].

However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].  Whether or not down regulation of *A*~n~ and reductions of growth are quantitavely similiar has rarely been tested.

Based on these previous studies, using a range of container sizes as a sink-strength manipulation can be used to empirically test the extent to which growth and *A*~n~ are coordinated.

@@

\
(1)
$$P_i = \frac{L_i~C_\mathrm{day'i}~\sigma - R_i}{\epsilon}$$

where *L*~i~ is modelled total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^). Total respiration was calculated as

\
(2)
$$R_i = \Sigma(R_\mathrm{c}~M_\mathrm{c,i})$$
where *R*~c~ is published or measured tissue respiration rates of each woody tissue component, including fine roots, coarse roots and stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass of each component (g). Leaf respiration is included in the calculation of *C*~day~ (described below). The change in individual component biomass (*M*~c,i~), here solved on a daily time step, is given by

>>>>

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
#install packages if not already installed
.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr",
                           "lme4", "lmerTest", "broom", "reporttools", "visreg")

# Install CRAN packages (if not already installed)
.inst <- .packages %in% installed.packages()
if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst], repos = "http://cran.at.r-project.org")

# Load packages into session
lapply(.packages, library, character.only=TRUE)

@@

\
An alternative experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating rooting volume, by varying the container size [@arp1991effects; @nesmith1998effect; @poorter2012pot]. Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root]. Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth]. A meta-analysis by Poorter et al. [-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used. This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect]. However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].  Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitavely similiar has rarely been tested. Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.

@@

\
(1)
$$P_i(t) = \frac{L_i(t-1)~Cday_i}~\sigma - R_i}{\epsilon}$$

where *L*~i~ is modelled total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), $\epsilon$ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R*~i~ is the mass based total respiration of all tissue components (g C d^-1^). Here, i represents model runs for each experimental treatment (1:7). Total respiration was calculated as

\
(2)
$$R_i(t) = \Sigma_{c=1}^{3}(R_\mathrm{c}~M_\mathrm{c,i})$$

where *R*~c~ is published or measured tissue respiration rates of each woody tissue component, including fine roots, coarse roots and stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and *M*~c,i~ is the modelled standing biomass of each component (g). Leaf respiration is included in the calculation of *C*~day~ (described below). The change in individual component biomass (*M*~c,i~), here solved on a daily time step, is given by
